Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2016-04-16 doc/GMP2015/revision_4/appendix_proofs.tex
Prepping for addendum

@@

    % Then, we can form a valid isostatic DR-plan $T_b$ from $T$. In $T_b$, $fanin(b)$is the number of leaves in the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $fanin(w)$ is the the number leaf nodes in the tree rooted at $w$, excluding the subtree constaining $b$, plus 1 (for the node leading to $b$).  Then, for any node $b$ that we choose, $T_b$ is a valid DR-plan. The size of $T_b$ will just be the maximum fanin of all nodes in $T_b$. Thus, if we want to minimize the size of our DR-plan, we simply need to take the $b$ that has the $T_b$ of smallest size.

@@

    For each node $b$, assign a size of the $T_b$ denoted $|T_b|$. $|T_b| = \displaystyle\max_{v \in T_b} fanin(v)$. We are looking for $b$ that minimizes $|T_b|$. Denote the sub-tree of $T$ rooted at $v$ by $T^v$ and the number of leaves in a tree $T$ by $nl(T)$. Note that $fanin(b)= nl(T^b)$ because no descendant of $b$ is isostatic. Similarly, for any ancestor $w$ of $b$, $fanin(w) = nl(T^w)-nl(T^{b'})+1$, where $b'$ is the child leading to $b$. All other nodes are not isostatic and hence do not appear in the isostatic DR-plan.
    % Then, we can form a valid isostatic DR-plan $T_b$ from $T$. In $T_b$, $b$'s children are now all of the leaf nodes of the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $w$'s children will be the node that leads to $b$, denoted $b'$, along with all of the other leaf nodes in the tree rooted at $w$, excluding $b'$. Then, for any node $b$ that we choose, $T_b$ is a valid DR-plan. The size of $T_b$ will just be the maximum fanin of all nodes in $T_b$. Thus, if we want to minimize the size of our DR-plan, we simply need to take the $b$ that has the $T_b$ of smallest size.

    The node to be pinned is always the the deepest nontrivial node of some path in $T$. Suppose a node $b$ is pinned that has a nontrivial child $v$. Then, $fanin_b(b) = nl(T^b) = nl(T^v) + n$, where $n$ is essentially the number of leaves between $b$ and $v$. If we had instead chosen to pin $v$, then $fanin_v(b) = nl(T^b) - nl(T^{b'}) + 1 \leq fanin_b(v)$. And for each ancestor $w$ of $b$, $fanin(w)$ is unchanged, meaning $|T_v| \leq |T_b|$. Thus we only have to check the deepest non-trivial nodes.

@@

    Suppose we pin 2 distinct nodes $v_i$ and $v_j$. Then, there must exist a common ancestor $a$ of $v_i$ and $v_j$. Then, in $T_{v_i,v_j}$, $fanin_{v_i,v_j}(a) = nl(T^a)$. However, if we chose to pin one of $v_i$ and $v_j$ twice, then $fanin_v(a) = nl(T^a) - nl(T^{a'}) +1$ . Thus $fanin_v(a)' \leq fanin_{v_i,v_j}(a)$. All ancestors of $a$ are unchanged. So $|T_v| \leq |T_{v_i,v_j}|$.

@@

    Thus, starting with a $T$ as described in the proof for Remark \ref{thm:1dofcase}, when a node $b$ is pinned, the same structure is preserved as before. Suppose  $v$ is an isostatic node after pinning $b$. Then, the children of $v$ (except one if $v \neq b$) have 1-dof. The realization complexity for $v$ is simply that of realizing each of its children. In general, the number of parameters for $v$  will be $np(v) = 4nc_1(v)+3$, if $v \neq b$ and $np(b) = 4nc_1(b)$, where $nc_k(v)$ is the number of $k$-dof children of $v$.

    Minimizing the algebraic complexity  requires minimizing the maximum $np(v)$ for any node $v$. In this case, it is not possible to always choose to pin a node closest to a leaf in the tree, because it could have high fan-in. So we  try
brute force by pinning all nodes to  pick the one with the lowest algebraic complexity. This algorithm is still quadratic for the 1-dof case.

    For the 2-dof situation, there are more cases to consider. If we pin the same node twice as above, we have $np(v) = 5nc_2(v)+3$ for any ancestor $v \neq b$ and $np(b) = 5nc_2(b)$. If we pin a node $v$ and one of its ancestors $v'$, then any nodes between $v'$ and $v$ will be 1-dof, any nodes above $v'$ will be isostatic, and nodes below $v$ will be 2-dof. Note that solving or realizing $v'$ will also realize $v$.  Next, we need to consider nodes above and including $v'$ in our complexity: $np(v') = 5nc_2(v') + 4$ and $np(a) = 3 + 5nc_2(a)$ for $a$ an ancestor of $v'$.

The only remaining case is pinning two nodes that are incomparable, i.e.\ do not have a descendant/ancestor relationship. The only change from the previous case is that for the lowest common ancestor of the nodes $v'$, $np(v') = 2*4+5nc_2(v')$. For any ancestor $a$ of $v'$, we still have $np(a) = 3 + 5nc_2(a)$.

>>>>

\newcommand{\faninx}[1]{\textsc{FanIn}(#1)}
\newcommand{\faninxy}[2]{\textsc{FanIn}_{#1}(#2)}
\newcommand{\numberofleavesx}[1]{\textsc{NL}(#1)}
\newcommand{\numberofparametersx}[1]{\textsc{NP}(#1)}
\newcommand{\numberofchildrenxy}[2]{\textsc{NC}_{#1}(#2)}

@@

    % Then, we can form a valid isostatic DR-plan $T_b$ from $T$. In $T_b$, $\faninx{b}$is the number of leaves in the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $\faninx{w}$ is the the number leaf nodes in the tree rooted at $w$, excluding the subtree containing $b$, plus 1 (for the node leading to $b$).  Then, for any node $b$ that we choose, $T_b$ is a valid DR-plan. The size of $T_b$ will just be the maximum fan-in of all nodes in $T_b$. Thus, if we want to minimize the size of our DR-plan, we simply need to take the $b$ that has the $T_b$ of smallest size.

@@

    For each node $b$, assign a size of the $T_b$ denoted $|T_b|$. $|T_b| = \displaystyle\max_{v \in T_b} \faninx{v}$. We are looking for $b$ that minimizes $|T_b|$. Denote the sub-tree of $T$ rooted at $v$ by $T^v$ and the number of leaves in a tree $T$ by $\numberofleavesx{T}$. Note that $\faninx{b}= \numberofleavesx{T^b}$ because no descendant of $b$ is isostatic. Similarly, for any ancestor $w$ of $b$, $\faninx{w} = \numberofleavesx{T^w}-\numberofleavesx{T^{b'}}+1$, where $b'$ is the child leading to $b$. All other nodes are not isostatic and hence do not appear in the isostatic DR-plan.
    % Then, we can form a valid isostatic DR-plan $T_b$ from $T$. In $T_b$, $b$'s children are now all of the leaf nodes of the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $w$'s children will be the node that leads to $b$, denoted $b'$, along with all of the other leaf nodes in the tree rooted at $w$, excluding $b'$. Then, for any node $b$ that we choose, $T_b$ is a valid DR-plan. The size of $T_b$ will just be the maximum fan-in of all nodes in $T_b$. Thus, if we want to minimize the size of our DR-plan, we simply need to take the $b$ that has the $T_b$ of smallest size.

    The node to be pinned is always the the deepest nontrivial node of some path in $T$. Suppose a node $b$ is pinned that has a nontrivial child $v$. Then, $\faninxy{b}{b} = \numberofleavesx{T^b} = \numberofleavesx{T^v} + n$, where $n$ is essentially the number of leaves between $b$ and $v$. If we had instead chosen to pin $v$, then $\faninxy{v}{b} = \numberofleavesx{T^b} - \numberofleavesx{T^{b'}} + 1 \leq \faninxy{b}{v}$. And for each ancestor $w$ of $b$, $\faninx{w}$ is unchanged, meaning $|T_v| \leq |T_b|$. Thus we only have to check the deepest non-trivial nodes.

@@

    Suppose we pin 2 distinct nodes $v_i$ and $v_j$. Then, there must exist a common ancestor $a$ of $v_i$ and $v_j$. Then, in $T_{v_i,v_j}$, $\faninxy{v_i,v_j}{a} = \numberofleavesx{T^a}$. However, if we chose to pin one of $v_i$ and $v_j$ twice, then $\faninxy{v}{a} = \numberofleavesx{T^a} - \numberofleavesx{T^{a'}} +1$ . Thus $\faninxy{v}{a}' \leq \faninxy{v_i,v_j}{a}$. All ancestors of $a$ are unchanged. So $|T_v| \leq |T_{v_i,v_j}|$.

@@

    Thus, starting with a $T$ as described in the proof for Remark \ref{thm:1dofcase}, when a node $b$ is pinned, the same structure is preserved as before. Suppose  $v$ is an isostatic node after pinning $b$. Then, the children of $v$ (except one if $v \neq b$) have 1-dof. The realization complexity for $v$ is simply that of realizing each of its children. In general, the number of parameters for $v$ will be $\numberofparametersx{v} = 4\numberofchildrenxy{1}{v}+3$, if $v \neq b$ and $\numberofparametersx{b} = 4\numberofchildrenxy{1}{b}$, where $\numberofchildrenxy{k}{v}$ is the number of $k$-dof children of $v$.

    Minimizing the algebraic complexity requires minimizing the maximum $\numberofparametersx{v}$ for any node $v$. In this case, it is not possible to always choose to pin a node closest to a leaf in the tree, because it could have high fan-in. So we try brute force by pinning all nodes to  pick the one with the lowest algebraic complexity. This algorithm is still quadratic for the 1-dof case.

    For the 2-dof situation, there are more cases to consider. If we pin the same node twice as above, we have $\numberofparametersx{v} = 5\numberofchildrenxy{2}{v}+3$ for any ancestor $v \neq b$ and $\numberofparametersx{b} = 5\numberofchildrenxy{2}{b}$. If we pin a node $v$ and one of its ancestors $v'$, then any nodes between $v'$ and $v$ will be 1-dof, any nodes above $v'$ will be isostatic, and nodes below $v$ will be 2-dof. Note that solving or realizing $v'$ will also realize $v$.  Next, we need to consider nodes above and including $v'$ in our complexity: $\numberofparametersx{v'} = 5\numberofchildrenxy{2}{v'} + 4$ and $\numberofparametersx{a} = 3 + 5\numberofchildrenxy{2}{a}$ for $a$ an ancestor of $v'$.

    The only remaining case is pinning two nodes that are incomparable, i.e.\ do not have a descendant/ancestor relationship. The only change from the previous case is that for the lowest common ancestor of the nodes $v'$, $\numberofparametersx{v'} = 2*4+5\numberofchildrenxy{2}{v'}$. For any ancestor $a$ of $v'$, we still have $\numberofparametersx{a} = 3 + 5\numberofchildrenxy{2}{a}$.

### 2016-04-16 doc/GMP2015/revision_4/s02_preliminaries.tex
Prepping for addendum

\subsubsection{Optimal Recursive Decomposition (DR-Planning)}
Recursive decomposition of geometric constraint systems has been formalized \cite{hoffman2001decompositionI,hoffman2001decompositionII} and well-studied \cite{lomonosov2004graph,sitharam2005combinatorial,jermann2006decomposition} as the \dfn {Decomposition-Recombination (DR-) planning} problem \seedefsprelim. For the abovementioned classes of 2D qusecs, generic rigidity is a combinatorial property and hence each level of the decomposition should, in principle, be achievable by a graph-based algorithm without involving the geometric information in the constraint system. Since many such decompositions can exist for a given constraint system, criteria defining desirable or optimal DR-plans and DR-planning algorithms were given in~\cite{hoffman2001decompositionI}.
%An \dfn{optimal DR-plan} is one that minimizes the \dfn{size} \seedefsprelim, i.e., the maximum number of child subsystems of any parent system. Being exponential in the size, the complexity of solving the parent constraint system is overwhelmingly dominated by the complexity of solving the child systems.

>>>>

\subsubsection{Optimal Recursive Decomposition (DR-Planning)}
Recursive decomposition of geometric constraint systems has been formalized \cite{hoffman2001decompositionI,hoffman2001decompositionII} and well-studied \cite{lomonosov2004graph,sitharam2005combinatorial,jermann2006decomposition} as the \dfn {Decomposition-Recombination (DR-) planning} problem \seedefsprelim. For the abovementioned classes of 2D qusecs, generic rigidity is a combinatorial property and hence each level of the decomposition should, in principle, be achievable by a graph-based algorithm without involving the geometric information in the constraint system. Since many such decompositions can exist for a given constraint system, criteria defining desirable or optimal DR-plans and DR-planning algorithms were given in~\cite{hoffman2001decompositionI}.
%
We conjecture (in Section~\ref{sec:open}) that one such decomposition, a version of \frontier~\cite{hoffman2001decompositionI, hoffman2001decompositionII,lomonosov2004graph,sitharam2005combinatorial}, which is a bottom-up, polynomial time method, also generates optimal DR-plans for independent systems.
% We additionally conjecture in Section~\ref{sec:open} that versions of \frontier, a previously given, bottom-up, polynomial time method for obtaining DR-plans with various desired properties~\cite{hoffman2001decompositionI, hoffman2001decompositionII,lomonosov2004graph,sitharam2005combinatorial}, in fact generate an optimal DR-plan for non-overconstrained systems.

%An \dfn{optimal DR-plan} is one that minimizes the \dfn{size} \seedefsprelim, i.e., the maximum number of child subsystems of any parent system. Being exponential in the size, the complexity of solving the parent constraint system is overwhelmingly dominated by the complexity of solving the child systems.

### 2016-04-16 doc/GMP2015/revision_4/s03_drp.tex
Prepping for addendum

\begin{lemma}
[\Branch\ leaves from components]
    Let $G$ be isostatic, $e$ be an edge in $G$, and $\componentsx{G\setminus e}$ be the set of maximal rigid components of $G\setminus e$. Then there is a \pseudosequential\ DR-plan $P_G$ for $G$ such that $\componentsx{G\setminus e}$ is exactly the set of leaves of \branchGePG\ (minus $e$ itself).
\end{lemma}

\begin{proof}
    Follows from the structure of a \pseudosequential\ DR-plan and the definition of \branchGePG.
\end{proof}

@@

\begin{lemma}
[\Branch\ from \branch\ leaves]
\label{lem:branch-from-branch-leaves}
    For an isostatic graph $G$ containing an edge $e$, the \branchGePG\ for a \pseudosequential\ DR-plan $P_G$ can be constructed from $\componentsx{G\setminus e}$, i.e.\ from the set of leaves of \branchGePG, by carrying out -- for each leaf $L$ -- one computation of $\componentsx{G\setminus f}$, where $f$ is any edge in $L$.
\end{lemma}

% \begin{proof}
%     First note that in order to obtain \branchGePG\ from the set of subgraphs at its leaves, it is sufficient to find the subgraphs at the nodes along the path from $e$ to $G$ in $P_G$. Once these non-leaf nodes of the \branch\ are known, the \branch\ leaves can be organized by parent node (and level) thereby obtaining the \branch.

%     Now observe that for a leaf $L$ and edge $f\in L$, there exists component $D\in \componentsx{G\setminus f}$ can be classified as one of the following cases.

%     Each case either discovers at least one node $C$ on the path from $e$ to $G$, and a sibling of $D$ in $P_G$, and partitions the leaves of \branchGePG\ into two sets, namely descendants of $C$ or children of ancestors of $C$; or finds a leaf of \branchLfPL\ ($\componentsx{L\setminus f}$ for the next recursion level of the algorithm).

%     % \todo{
%     % Case (0):
%     % $D$ is exactly some component $C$ of $\componentsx{G\setminus e}$.... The only true 1a is the leftmost in subfig 2, everything else is 0... In this case, we know $C=D$ to be some child of an ancestor of $C$.
%     % }

%     Case (1):
%     $D$ contains some components $C$ of $\componentsx{G\setminus e}$ (i.e.\ leaves of \branchGePG) and intersects all other leaves of \branchGePG\ trivially. One occurrence of this case (Case 1a) is when $L$'s siblings in (any \pseudosequential\ DR-plan) $P_G$ have trivial pairwise intersection. Another occurrence of this case (Case 1b) is when $L$'s siblings in (any \pseudosequential\ DR-plan) $P_G$ have non-trivial pairwise intersections, but the edge $f$ is in their common intersection, i.e.\ the core \todo{mentions core!}. In both cases, $D$ is a node along the path from $e$ to $G$ in $P_G$, with the components $C$ being its descendants, $L$ being its sibling and all other components in $\componentsx{G\setminus e}$ (i.e.\ leaves of \branchGePG) being children of $D$'s ancestors in \branchGePG.
%     \todo{(1c), it contains no components.}

%     Case (2):
%     $D$ is contained in $L$ and intersects all other leaves of \branchGePG\ trivially. In this case, $D$ is a leaf of \branchLfPL, to be used in the next level recursion of the algorithm.

%     Case (3):
%     $D$ intersects $L$ non-trivially, neither contains nor is contained in $L$, but contains some components $C$ of $\componentsx{G\setminus e}$ (leaves of \branchGePG). This happens when the siblings of $L$ in a canonical DR-plan for $G$ intersect $L$ non-trivially. In this case, $D\cup L$ is a node along the path from $e$ to $G$ with the components $C$ being its descendants, $L$ being its  child and all other components in $\componentsx{G\setminus e}$ (i.e.\ leaves of \branchGePG) being children of $D$'s ancestors in \branchGePG. In addition, $D\cap L$ is a leaf of \branchLfPL\ to be used in the next recursion level of the algorithm.

%     One subtle obstacle to overcome in Case 3 is that the newly found node along the path from $e$ to $G$ is the parent of $L$ as opposed to a sibling of $L$ as in Case (1). On the surface, this is problematic because the sibling $D'$ of $L$ along the path from $e$ to $G$ may never be found. However a closer inspection of Case 3 reveals that $L$ is the partner of an appendage $A$ containing $e$, and $A$, being underconstrained by Observation~\ref{lemma:union_intersection} and Lemma~\ref{lemma:combined_lemma}, must have maximal rigid components with nontrivial intersections, which means that there must be another sibling of $D'$ that is a leaf $L'$ of \branchGePG. Hence for some edge $f'$ in $L'$, $\componentsx{G\setminus f'}$ will find $D'$ within Case 1.

%     Since each node along the path from $e$ to $G$ is found by the above procedure, the proof is complete.
% \end{proof}

\begin{proof}
    First note that in order to obtain \branchGePG\ from the set of subgraphs at its leaves, it is sufficient to find the subgraphs at the nodes along the path from $G$ to $e$ in $P_G$. Once these non-leaf nodes of the \branch\ are known, the \branch\ leaves can be organized by parent node (and level) thereby obtaining the \branch.

    For a leaf $L$ and edge $f\in L$, we can classify the component $D\in \componentsx{G\setminus f}$ as being one of the following cases:

    Case (1):
    $D$ and $L$ are edge disjoint, and $D$ contains
    (1a) no elements,
    (1b) exactly one element, or
    % originally 1a and 1b
    (1c) more than one element
    of $\componentsx{G\setminus e}$.
    %
    Case (2):
    $D$ and $L$ have non-empty intersection of edge sets, and $D$ is
    % originally 2
    (2a)
    a proper subgraph or
    % originally 3
    (2b)
    not a subgraph
    of $L$.
    %
    Note that this list is exhaustive. If $D$ and $L$ are edge disjoint, $D$ cannot contain subgraphs of elements of $\componentsx{G\setminus e}$. If $D$ and $L$ have non-empty intersection of edge sets, $D$ cannot be exactly $L$.

@@

    Case (1a) implies that $D=e$, and is therefore a sibling of $L$ and an element on the path from $G$ to $e$. Furthermore, we can classify the rest of the leaves (i.e.\ $\componentsx{G\setminus e}$) as children of the ancestors of $D$.

    Similarly, Case (1c) implies that $D$ is a sibling of $L$ on the path from $G$ to $e$. It also allows us to partition the leaves as either children of $L$ (those components which are subgraphs of $D$) or as children of the ancestors of $D$. This case occurs when the siblings of $L$ in (any \pseudosequential\ DR-plan) $P_G$ have either (1c1) trivial pairwise intersection or (1c2) non-trivial pairwise intersections, but the edge $f$ is in their common intersection, i.e.\ the core.

    Case (2a) implies that $D$ is a leaf in \branchLfPL\ to be used in the next level of recursion of the algorithm.

@@

    % Since each level of \branchGePG\ will contain some $L$ and $f\in L$ with a $D\in \componentsx{G\setminus f}$ that is either of Case (1a), (1c), or (2b) all nodes in the path from $G$ to $e$ can be found, which completes the proof.
    Since each node along the path from $G$ to $e$ is found by the above procedure, the proof is complete.
    See Figure~\ref{fig:seq_proof} for examples of the cases.
\end{proof}

>>>>

\begin{lemma}
[\Branch\ leaves from components]
\label{lem:leaves-from-comps}
    Let $G$ be isostatic, $e$ be an edge in $G$, and $\componentsx{G\setminus e}$ be the set of maximal rigid components of $G\setminus e$. Then there is a \pseudosequential\ DR-plan $P_G$ for $G$ such that each element in the set of leaves of \branchGePG\ (except $e$ itself) is a subgraph of exactly one element in $\componentsx{G\setminus e}$.
\end{lemma}

\begin{proof}
    By definition, the leaves of \branchGePG\ are pairwise disjoint, as are the elements of $\componentsx{G\setminus e}$. Furthermore, $E(G)$ is equal to the union of the leaves of \branchGePG\ is equal to the union of $\componentsx{G\setminus e}$ and $\{ e \}$.

    We show that there is no leaf that has a non-empty intersection with two or more elements of $\componentsx{G\setminus e}$, proving the lemma. Assume that such a leaf $L$ exists. If there were some component $C$ such that $L\cap C$ were non-trivial, then $L\cup C\neq C$ would be isostatic, contradicting the assumption that $C$ was maximal. If, for all components $C$ that $L$ intersects, $C\cap L$ is trivial, then none of the edges in $L$ are contained in $\componentsx{G\setminus e}$, again a contradiction.
\end{proof}

\begin{observation}
     If there is no proper isostatic subgraph of $G$ that (i) contains $e$ and at least one component of $G\setminus e$ and (ii) intersects another component non-trivially, then $\componentsx{G\setminus e}\cup \{ e\}$ is exactly the set of leaves of \branchGePG\
\end{observation}

@@

% \begin{lemma}
% [\Branch\ from \branch\ leaves]
% \label{lem:branch-from-branch-leaves}
%     For an isostatic graph $G$ containing an edge $e$, the \branchGePG\ for a \pseudosequential\ DR-plan $P_G$ can be constructed from $\componentsx{G\setminus e}$, i.e.\ from the set of leaves of \branchGePG, by carrying out -- for each leaf $L$ -- one computation of $\componentsx{G\setminus f}$, where $f$ is any edge in $L$.
% \end{lemma}

\begin{lemma}
[\Branch\ from \branch\ leaves]
\label{lem:branch-from-branch-leaves}
    For an isostatic graph $G$ containing an edge $e$, the \branchGePG\ for a \pseudosequential\ DR-plan $P_G$ can be constructed from $\componentsx{G\setminus e}$ by carrying out -- for each component $C$ -- one computation of $\componentsx{G\setminus f}$, where $f$ is any edge in $C$.
\end{lemma}

\begin{proof}
    First, note that in order to obtain \branchGePG\ from the set of subgraphs at its leaves, it is sufficient to find the subgraphs at the nodes along the path from $G$ to $e$ in $P_G$. Once these non-leaf nodes of the \branch\ are known, the \branch\ leaves can be organized by parent node (and level) thereby obtaining the \branch.

    Second, note that by Lemma~\ref{lem:leaves-from-comps}, exactly two cases can arise: either (A) $\componentsx{G\setminus e}$ is exactly the set of leaves of \branchGePG\ (except $e$ itself); or, (B) there are some elements of $\componentsx{G\setminus e}$ that are exactly the union of two or more leaves (except $e$). We begin by describing case (A).

    For a component $C$ and edge $f\in C$, we can classify the component $D\in \componentsx{G\setminus f}$ as being one of the following cases:

    Case (1):
    $C$ and $D$ are edge disjoint, and $D$ contains
    (1a) no elements,
    (1b) exactly one element (and is equal to this element), or
    % originally 1a and 1b
    (1c) more than one element (and is equal to the union of these elements)
    of $\componentsx{G\setminus e}$.
    %
    Case (2):
    $C$ and $D$ have non-empty intersection of edge sets, and $D$ is
    % originally 2
    (2a) a proper subgraph or
    % originally 3
    (2b) not a subgraph
    of $C$.
    %
    Note that this list is exhaustive. If $C$ and $D$ are edge disjoint, $D$ cannot contain a subgraph of an element of $\componentsx{G\setminus e}$.
    % Suppose there were some other component $C'$ such that $C'\cap D$ was non-empty and did not equal $C'$. If the intersection were non-trivial
    % intersected f the intersection This would imply a larger isostatic graph
    If $D$ and $L$ have non-empty intersection of edge sets, $D$ cannot be exactly $L$.

    % Now observe that, given case (1), it is implied that $C$ is in fact a leaf in \branchGePG. If it were the union of several leaves, then the $f$ we chose would come from one such leaf

@@

    Case (1a) implies that $D=e$, and is therefore a sibling of $C$ and an element on the path from $G$ to $e$. Furthermore, we can classify the rest of $\componentsx{G\setminus e}$ as components that contain only leaves that are children of the ancestors of $D$.

    Similarly, Case (1c) implies that $D$ is a sibling of $C$ on the path from $G$ to $e$. It also allows us to partition the rest of $\componentsx{G\setminus e}$ as either descendants of $C$ (those components which are subgraphs of $D$) or as children of the ancestors of $D$. This case occurs when the siblings of $C$ in (any \pseudosequential\ DR-plan) $P_G$ have either (1c1) trivial pairwise intersection or (1c2) non-trivial pairwise intersections, but the edge $f$ is in their common intersection, i.e.\ the core.

    Case (2a) implies that $D$ is a component whose constituent leaves are leaves in \branchLfPL\ to be used in the next level of recursion of the algorithm.
    % Case (2a) implies that $D$ is in $\componentsx{C\setminus f}$, to be used in the next level of recursion of the algorithm.

@@

    % !!!!!!!
    However, if $D$ contains $e$...
    This implies that $C\cap D$ is a leaf of \branchGePG. Now choose a new $f'\in (C\setminus D)$ and repeat the above process (classifying all the $D'\in \componentsx{G\setminus f'}$ based on their intersections with $C'=(C\setminus D)$).

    % Since each level of \branchGePG\ will contain some $L$ and $f\in L$ with a $D\in \componentsx{G\setminus f}$ that is either of Case (1a), (1c), or (2b) all nodes in the path from $G$ to $e$ can be found, which completes the proof.
    Since each node along the path from $G$ to $e$ is found by the above procedure, the proof of case (A) is complete.
    See Figure~\ref{fig:seq_proof} for examples of the cases.

    Case (B). We apply the process recursively to the component that is the union of some subset of the leaves. This is guaranteed to terminate (at some level of recursion we will be dealing with only case (A)). Once we have the DR-plan of the leaf, we rearrange it such that the relevant piece is on the last level. Then we merge it into the branch we were trying to build.

    Since either case requires the decomposition of each leaf, we can detect at this time whether or not this is an instance of case (A) or (B).
\end{proof}

### 2016-04-16 doc/GMP2015/revision_4/s04_recombination.tex
Prepping for addendum

\subsection{Using Convex Cayley Configuration Spaces}
\label{sec:2-tree-reduction}
%
Next we provide the necessary background to describe a specific approach for achieving the requirements (a)--(c) mentioned above, by restricting the class of reduced graphs $G' = G\setminus E_1$ and their isostatic completions $H$ in the above definition of the OMD problem, and using a key theorem of Convex Cayley configuration spaces \cite{sitharam2010convex}. This theorem characterizes the class of graphs $H$ and non-edges $F$ (Cayley parameters), such that the set of vectors $\lambda_F$ of  attainable lengths of the non-edges $F$ is always convex for any given lengths $\delta$ for the edges of $H$ (i.e.\ over all the realizations of the bar-joint constraint system or linkage $(H,\delta)$ in 2 dimensions). This set is called the (2-dimensional) \dfn{Cayley configuration space} of the linkage $(H,\delta)$ on the Cayley parameters $F$, denoted $\Phi_F(H,\delta)$ and can be viewed as a ``projection'' of the cartesian realization space of $(H,\delta)$ on the Cayley parameters $F$. Such graphs $H$ are said to have \dfn{convexifiable Cayley configuration spaces for some parameters $F$} (short: $H$ is \dfn{convexifiable}).

@@

% \begin{proof}
%     The Cartesian realization space of $(H,\left<\delta_{E'},
%     \lambda_F\right>)$ is computed easily with a DR-plan of size 2,
%     and is the union of $2^t$ solutions (modulo orientation preserving
%     isometries) each with a distinct orientation type, where $t$ is
%     the number of triangles in the 2-tree $H$; here $\delta_{S}$ is
%     the restriction of the length vector $\delta$ to the edges in $S$.
%     A desired solution $p$ (or connected component of a solution
%     space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be
%     found by a subdivided binary search   of the cartesian realization
%     space of $(H, \left<\delta_{E'}, \lambda_F\right>)$ of orientation
%     type $\sigma_p$ - as $\lambda_F$ ranges over the discretized
%     convex polytope $\Phi_F(G',\delta_E')$ with bounding hyperplanes
%     described in Theorem \ref{theorem:convexcayley}. A solution $p$
%     is found  when the lengths for nonedges in $D$ match $\delta_D$.
% \end{proof}
%
% \begin{figure*}\centering
% \begin{subfigure}{.2\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example_new-0.tikz}
%     \caption{}\label{fig:omd_k33_example:a}
% \end{subfigure}\hfill
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example_new-1.tikz}
%     \caption{}\label{fig:omd_k33_example:b}
% \end{subfigure}
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example_new-2.tikz}
%     \caption{}\label{fig:omd_k33_example:c}
% \end{subfigure}\hfill
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example-1.tikz}
%     \caption{}\label{fig:omd_k33_example:d}
% \end{subfigure}
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example-2.tikz}
%     \caption{}\label{fig:omd_k33_example:e}
% \end{subfigure}

>>>>

\subsection{Using Convex Cayley Configuration Spaces}
\label{sec:2-tree-reduction}
%
Next we provide the necessary background to describe a specific approach for achieving the requirements (a)--(c) mentioned above, by restricting the class of reduced graphs $G' = G\setminus E_1$ and their isostatic completions $H$ in the above definition of the OMD problem, and using a key theorem of Convex Cayley configuration spaces \cite{sitharam2010convex}. This theorem characterizes the class of graphs $H$ and non-edges $F$ (Cayley parameters), such that the set of vectors $\lambda_F$ of  attainable lengths of the non-edges $F$ is always convex for any given lengths $\delta$ for the edges of $H$ (i.e.\ over all the realizations of the bar-joint constraint system or linkage $(H,\delta)$ in 2 dimensions). This set is called the (2-dimensional) \dfn{Cayley configuration space} of the linkage $(H,\delta)$ on the Cayley parameters $F$, denoted $\Phi_F(H,\delta)$ and can be viewed as a ``projection'' of the Cartesian realization space of $(H,\delta)$ on the Cayley parameters $F$. Such graphs $H$ are said to have \dfn{convexifiable Cayley configuration spaces for some parameters $F$} (short: $H$ is \dfn{convexifiable}).

@@

% \begin{proof}
%     The Cartesian realization space of $(H,\left<\delta_{E'},
%     \lambda_F\right>)$ is computed easily with a DR-plan of size 2,
%     and is the union of $2^t$ solutions (modulo orientation preserving
%     isometries) each with a distinct orientation type, where $t$ is
%     the number of triangles in the 2-tree $H$; here $\delta_{S}$ is
%     the restriction of the length vector $\delta$ to the edges in $S$.
%     A desired solution $p$ (or connected component of a solution
%     space) of $(G,\delta)$ of an orientation type $\sigma_p$ can be
%     found by a subdivided binary search   of the Cartesian realization
%     space of $(H, \left<\delta_{E'}, \lambda_F\right>)$ of orientation
%     type $\sigma_p$ - as $\lambda_F$ ranges over the discretized
%     convex polytope $\Phi_F(G',\delta_E')$ with bounding hyperplanes
%     described in Theorem \ref{theorem:convexcayley}. A solution $p$
%     is found  when the lengths for nonedges in $D$ match $\delta_D$.
% \end{proof}
%
% \begin{figure*}\centering
% \begin{subfigure}{.2\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example_new-0.tikz}
%     \caption{}\label{fig:omd_k33_example:a}
% \end{subfigure}\hfill
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example_new-1.tikz}
%     \caption{}\label{fig:omd_k33_example:b}
% \end{subfigure}
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example_new-2.tikz}
%     \caption{}\label{fig:omd_k33_example:c}
% \end{subfigure}\hfill
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example-1.tikz}
%     \caption{}\label{fig:omd_k33_example:d}
% \end{subfigure}
% \begin{subfigure}{.15\linewidth}\centering
%     \input{../../img/tikz/omd_k33_example-2.tikz}
%     \caption{}\label{fig:omd_k33_example:e}
% \end{subfigure}

### 2016-04-16 doc/GMP2015/revision_4/s07_pinnedline.tex
Prepping for addendum

\section{Application: Finding Optimal DR-Plans and Realizations for Cross-Linking Microfibrils }
\label{sec:pinnedline}

@@

Figure~\ref{fig:pinned_line} shows an example of a pinned line-incidence graph, where the grey ovals denote pins representing attachments of fibrils, and the vertices $a_1,a_2,\ldots, c_3$ represent cross-linkings.
% and the black dots stand for vertices/cross-linkings.
%There are  and 10 vertices/cross-linkings in the graph.
The graph is isostatic, with 12 vertices and 24 edges/pins.

>>>>

\section{Application: Finding Optimal DR-Plans and Realizations for Cross-Linking Microfibrils}
\label{sec:pinnedline}

@@

Figure~\ref{fig:pinned_line} shows an example of a pinned line-incidence graph, where the gray ovals denote pins representing attachments of fibrils, and the vertices $a_1,a_2,\ldots, c_3$ represent cross-linkings.
% and the black dots stand for vertices/cross-linkings.
%There are  and 10 vertices/cross-linkings in the graph.
The graph is isostatic, with 12 vertices and 24 edges/pins.
